Reproducible Research in R: A Tutorial on how to Do the Same Thing More Than Once

### 2021-11-23 manuscript.Rmd
remove false dichotomy most conformatory analyses are aimed at discovering patterns -> weak theories
missing word

*Preregistration* refers to the practice of defining research questions and planning data analysis before observing the research outcomes [@NosekRevolution2018].
It serves to separate a-priori planned and theory-driven (confirmatory) analyses from unplanned and post-hoc (exploratory) analyses.
Exploratory analyses refer to both those aimed at discovering patterns in data, and those aimed at overcoming shortcomings of confirmatory analyses that come to light after seeing the data (e.g., violations of assumptions, modifications to address poor model fit).
Researchers are faced with a myriad of choices in designing, executing, and analyzing a study, often called researchers degrees of freedom.
Undisclosed researcher degrees may be used to modify planned analyses until a key finding reaches statistical significance or to inflate effect size estimates, a phenomenon referred to as *opportunistic bias* [@decosterOpportunisticBiasesTheir2015].
Preregistration increases transparency by clarifying when and how researchers employ their degrees of freedom.
It expressly does not restrict what researchers may do to gather or analyze their data.

@@

Another common misunderstanding is that preregistration, including PAC, precludes exploratory analyses.
We differentiate between two kinds of exploration, neither of which is limited by PAC.
The first, more traditional kind of exploration involves ad hoc statistical decisions and post hoc explanations of the results.
Such traditional exploratory findings should be explicitly declared in the manuscript to distinguish them from confirmatory findings [@NosekRevolution2018; @nosekPreregistrationHardWorthwhile2019].
The second kind of exploration is through procedurally well defined exploration with exploratory statistical models are standard in machine learning [@brandmaier22mlsem].
These models often involve dozens, if not hundreds of predictors, which makes it difficult to describe them verbally.
With PAC, such models can be preregistered clearly and in comprehensive detail and researcher can precisely define a priori how much they want to explore.
We specifically recommend PAC for such exploratory statistical models.
The merit of preregistration in these cases is to communicate precisely how much exploration was done;
a piece of information that is crucial to assess e.g., whether the results might be overfit [@hastieElementsStatisticalLearning2017, p. 220f.].

>>>>

*Preregistration* refers to the practice of defining research questions and planning data analysis before observing the research outcomes [@NosekRevolution2018].
It serves to separate a-priori planned and theory-driven (confirmatory) analyses from unplanned and post-hoc (exploratory) analyses.
Researchers are faced with a myriad of choices in designing, executing, and analyzing a study, often called researchers degrees of freedom.
Undisclosed researcher degrees may be used to modify planned analyses until a key finding reaches statistical significance or to inflate effect size estimates, a phenomenon referred to as *opportunistic bias* [@decosterOpportunisticBiasesTheir2015].
Preregistration increases transparency by clarifying when and how researchers employ their degrees of freedom.
It expressly does not restrict what researchers may do to gather or analyze their data.

@@

Another common misunderstanding is that preregistration, including PAC, precludes exploratory analyses.
We differentiate between two kinds of exploration, neither of which is limited by PAC.
The first, more traditional kind of exploration involves ad hoc statistical decisions and post hoc explanations of the results.
Such traditional exploratory findings should be explicitly declared in the manuscript to distinguish them from confirmatory findings [@NosekRevolution2018; @nosekPreregistrationHardWorthwhile2019].
The second kind of exploration is through procedurally well defined exploration with exploratory statistical models that are standard in machine learning [@brandmaier22mlsem].
These models often involve dozens, if not hundreds of predictors, which makes it difficult to describe them verbally.
With PAC, such models can be preregistered clearly and in comprehensive detail and researcher can precisely define a priori how much they want to explore.
We specifically recommend PAC for such exploratory statistical models.
The merit of preregistration in these cases is to communicate precisely how much exploration was done;
a piece of information that is crucial to assess e.g., whether the results might be overfit [@hastieElementsStatisticalLearning2017, p. 220f.].
